Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-10 automatica/paper.tex
section 8

Our benchmark suite consists of 26 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sample times, leading to $191$ different benchmarks
to evaluate the Na\"ive (Multi-staged) and Abstraction-based CEGIS approaches.

The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
underactuated robot manipulator, named acrobot, linearized by partial 
feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} (\#3) plant corresponds to the discrete model of a simple 
eletromagnet-ball system, where a steel ball is levitated in air by the action 
of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
The \textit{bioreactor} benchmark (\#4) is a linear model identified by least squares 
for the cell mass concentration controlled through dilution rate of a 
bioreactor~\cite{bioreactor}.

The \textit{Chen\_ex1}, \textit{Chen\_ex2}, \textit{Chen\_ex3} and \textit{Chen\_ex4} 
benchmarks (\#5-8) correspond to high-order control system discrete models generally used as 
case study for model order reduction techniques~\cite{CHEN1979389}. The benchmarks 
\textit{Cruise}~\cite{Franklin15} (\#9) and \textit{CruiseHSCC}~\cite{Astrom08} (\#10) are 
automotive cruise control models. Automotive cruise control is used to keep 
constant the speed of an automobile, tracking a desired speed reference, 
compensating disturbances and uncertainties related to relief and terrain.

There are two continuous stirred tank reactor models named \textit{cstr} (\#11) and 
\textit{cstrtmp} (\#12), which describe the PH dynamics of a neutralization reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
flow stirred-tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
dynamics of a basic brushed direct current electrical machine.

>>>>

Our benchmark suite consists of 26 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sampling times, 
leading to $191$ different benchmarks to evaluate the Multi-staged and Abstraction-based CEGIS algorithms.

The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
underactuated robot manipulator, 
%named acrobot, 
linearized by partial feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} (\#3) plant corresponds to the model of a simple 
eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
The \textit{bioreactor} benchmark (\#4) is a linear model 
%identified by least squares 
of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.

The \textit{Chen\_ex1}, \textit{Chen\_ex2}, \textit{Chen\_ex3} and \textit{Chen\_ex4} 
benchmarks (\#5-8) correspond to high-order control system 
%discrete 
models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}. 
The benchmarks \textit{Cruise}~\cite{Franklin15} (\#9) and \textit{CruiseHSCC}~\cite{Astrom08} (\#10) deal with 
automotive cruise control models, where control is used to keep 
constant the speed of an automobile, tracking a desired speed reference, and compensating disturbances and uncertainties. % related to relief and terrain.

%There are two continuous stirred tank reactor models named 
\textit{cstr} (\#11) and \textit{cstrtmp} (\#12) describe the PH dynamics of a neutralization reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
flow stirred-tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
dynamics of a basic brushed direct current electrical machine.
